### 2022-10-15 draft.tex
Deploying to gh-pages from @ gottacatchenall/ms_false_negatives@80920980ebd5187ab667cfd01f41e41cfcdd9132 🚀

%
\href{https://orcid.org/0000-0002-6506-6487}{Michael D.\,Catchen}%
%
\,\textsuperscript{,}\quad %
\href{https://orcid.org/0000-0002-0735-5184}{Timothée\,Poisot}%
%
\,\textsuperscript{,}\quad %
\href{https://orcid.org/0000-0002-6004-4027}{Laura\,Pollock}%
%
\,\textsuperscript{,}\quad %
\href{https://orcid.org/0000-0001-6075-8081}{Andrew\,Gonzalez}%
%
\,\textsuperscript{,}

@@

@@

\hypertarget{tbl:id}{}
\begin{longtable}[]{@{}
  >{\centering\arraybackslash}p{(\columnwidth - 16\tabcolsep) * \real{0.3182}}
  >{\centering\arraybackslash}p{(\columnwidth - 16\tabcolsep) * \real{0.1705}}
  >{\centering\arraybackslash}p{(\columnwidth - 16\tabcolsep) * \real{0.0568}}
  >{\centering\arraybackslash}p{(\columnwidth - 16\tabcolsep) * \real{0.0568}}
  >{\centering\arraybackslash}p{(\columnwidth - 16\tabcolsep) * \real{0.0795}}
  >{\centering\arraybackslash}p{(\columnwidth - 16\tabcolsep) * \real{0.0795}}
  >{\centering\arraybackslash}p{(\columnwidth - 16\tabcolsep) * \real{0.0795}}
  >{\centering\arraybackslash}p{(\columnwidth - 16\tabcolsep) * \real{0.0795}}
  >{\centering\arraybackslash}p{(\columnwidth - 16\tabcolsep) * \real{0.0795}}@{}}
\caption{\label{tbl:id}This table describes the datasets used in the
above analysis (Fig 2). The table reports the type of each dataset, the
total number of networks in each dataset \((N)\), the total species
richness in each dataset \((S)\), the connectance of each metaweb (all
interactions across the entire spatial-temporal extent) \((C)\), the
mean species richness across each local network \(S\), the mean
connectance of each local network \(C\), the mean \(\beta\)-diversity
among overlapping species across all pairs of network species
(\(\bar{\beta}_{OS}\)), and the mean \(\beta\)-diversity among all
species in the metaweb (\(\bar{\beta}_{WN}\)). Both metrics are computed
using KGL \(\beta\)-diversity (Koleff \emph{et al.}
2003)}\tabularnewline
\toprule()
\begin{minipage}[b]{\linewidth}\centering
Network
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Type
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
\(N\)
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
\(S\)
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
\(C\)
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
\(\bar{S}\)
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
\(\bar{C}\)
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
\(\bar{\beta}_{OS}\)
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
\(\bar{\beta}_{WN}\)
\end{minipage} \\
\midrule()
\endfirsthead
\toprule()
\begin{minipage}[b]{\linewidth}\centering
Network
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Type
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
\(N\)
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
\(S\)
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
\(C\)
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
\(\bar{S}\)
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
\(\bar{C}\)
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
\(\bar{\beta}_{OS}\)
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
\(\bar{\beta}_{WN}\)
\end{minipage} \\
\midrule()
\endhead
Kopelke \emph{et al.} (2017) & Food Web & 100 & 98 & 0.037 & 7.87 &
0.142 & 1.383 & 1.972 \\
Thompson \& Townsend (2000) & Food Web & 18 & 566 & 0.014 & 80.67 &
0.049 & 1.617 & 1.594 \\
Havens (1992) & Food Web & 50 & 188 & 0.065 & 33.58 & 0.099 & 1.468 &
1.881 \\
Ponisio \emph{et al.} (2017) & Pollinator & 100 & 226 & 0.079 & 23.0 &
0.056 & 1.436 & 1.870 \\
Hadfield \emph{et al.} (2014) & Host-Parasite & 51 & 327 & 0.085 & 32.71
& 0.337 & 1.477 & 1.952 \\
Closs \& Lake (1994) & Food Web & 12 & 61 & 0.14 & 29.09 & 0.080 & 1.736
& 1.864 \\
CaraDonna \emph{et al.} (2017) & Pollinator & 86 & 122 & 0.18 & 21.42 &
0.312 & 1.527 & 1.907 \\
\bottomrule()
\end{longtable}

@@

A better understanding of how false-negatives impact our inference of
network structure and dynamics is prediction of ecological networks by
both using information about individual species interactions and the
structure of metawebs on large scales is a practical necessity.
False-negatives could pose a problem for many forms of inference in
network ecology. For example, inferring the structural or dynamic
stability of a network could be prone to error if the observed network
is not sampled ``enough''. What exactly ``enough'' means is then
specific to the application, and should be assessed via methods like
those here when designing samples. Further, predictions about network
rewiring (Thompson \& Gonzalez 2017) due to range shifts in response to
climate change could be error-prone without accounting for interactions
that have not been observed but that still may become climatically
infeasible. As is evident from Figure 1(A), we can never guarantee there
are no false-negatives in data. In recent years, there has been interest
toward explicitly accounting for false-negatives in models (Stock
\emph{et al.} 2017; Young \emph{et al.} 2021), and a predictive approach
to networks---rather than expecting our samples to fully capture all
interactions (Strydom \emph{et al.} 2021). As a result, better models
for predicting interactions are needed for interaction networks. This
includes explicitly accounting for observation error (Johnson \&
Larremore 2021)---certain classes of models have been used to reflect
hidden states which account for detection error in occupancy modeling
(Joseph 2020), and could be integrated in the predictive models of
interactions in the future.

@@

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-Banville2021ManJl}{}}%
Banville, F., Vissault, S. \& Poisot, T. (2021).
\href{https://doi.org/10.21105/joss.02721}{Mangal.jl and
EcologicalNetworks.jl: Two complementary packages for analyzing
ecological networks in Julia}. \emph{Journal of Open Source Software},
6, 2721.

\leavevmode\vadjust pre{\hypertarget{ref-Bascompte2007PlaMut}{}}%
Bascompte, J. \& Jordano, P. (2007).
\href{https://doi.org/10.1146/annurev.ecolsys.38.091206.095818}{Plant-Animal
Mutualistic Networks: The Architecture of Biodiversity}. \emph{Annual
Review of Ecology, Evolution, and Systematics}, 38, 567--593.

\leavevmode\vadjust pre{\hypertarget{ref-Becker2021OptPre}{}}%
Becker, D.J., Albery, G.F., Sjodin, A.R., Poisot, T., Bergner, L.M.,
Dallas, T.A., \emph{et al.} (2021).
\href{https://doi.org/10.1101/2020.05.22.111344}{Optimizing predictive
models to prioritize viral discovery in zoonotic reservoirs}.

\leavevmode\vadjust pre{\hypertarget{ref-Bezanson2015JulFre}{}}%
Bezanson, J., Edelman, A., Karpinski, S. \& Shah, V.B. (2015).
\href{https://doi.org/10.48550/arXiv.1411.1607}{Julia: A Fresh Approach
to Numerical Computing}.

\leavevmode\vadjust pre{\hypertarget{ref-Blanchet2020CooNot}{}}%
Blanchet, F.G., Cazelles, K. \& Gravel, D. (2020).
\href{https://doi.org/10.1111/ele.13525}{Co-occurrence is not evidence
of ecological interactions}. \emph{Ecology Letters}, 23, 1050--1063.

\leavevmode\vadjust pre{\hypertarget{ref-Blaom2020MljJul}{}}%
Blaom, A.D., Kiraly, F., Lienart, T., Simillides, Y., Arenas, D. \&
Vollmer, S.J. (2020). \href{https://doi.org/10.21105/joss.02704}{MLJ: A
Julia package for composable machine learning}. \emph{Journal of Open
Source Software}, 5, 2704.

\leavevmode\vadjust pre{\hypertarget{ref-Boakes2015InfSpe}{}}%
Boakes, E.H., Rout, T.M. \& Collen, B. (2015).
\href{https://doi.org/10.1111/2041-210X.12365}{Inferring species
extinction: The use of sighting records}. \emph{Methods in Ecology and
Evolution}, 6, 678--687.

\leavevmode\vadjust pre{\hypertarget{ref-Canard2012EmeStr}{}}%
Canard, E., Mouquet, N., Marescot, L., Gaston, K.J., Gravel, D. \&
Mouillot, D. (2012).
\href{https://doi.org/10.1371/journal.pone.0038295}{Emergence of
Structural Patterns in Neutral Trophic Networks}. \emph{PLOS ONE}, 7,
e38295.

\leavevmode\vadjust pre{\hypertarget{ref-CaraDonna2017IntRew}{}}%
CaraDonna, P.J., Petry, W.K., Brennan, R.M., Cunningham, J.L.,
Bronstein, J.L., Waser, N.M., \emph{et al.} (2017).
\href{https://doi.org/10.1111/ele.12740}{Interaction rewiring and the
rapid turnover of plantpollinator networks}. \emph{Ecology Letters}, 20,
385--394.

\leavevmode\vadjust pre{\hypertarget{ref-Carlson2020WhaWou}{}}%
Carlson, C.J., Dallas, T.A., Alexander, L.W., Phelan, A.L. \& Phillips,
A.J. (2020). \href{https://doi.org/10.1098/rspb.2020.1841}{What would it
take to describe the global diversity of parasites?} \emph{Proceedings
of the Royal Society B: Biological Sciences}, 287, 20201841.

\leavevmode\vadjust pre{\hypertarget{ref-Cazelles2016TheSpe}{}}%
Cazelles, K., Araújo, M.B., Mouquet, N. \& Gravel, D. (2016).
\href{https://doi.org/10.1007/s12080-015-0281-9}{A theory for species
co-occurrence in interaction networks}. \emph{Theoretical Ecology}, 9,
39--48.

\leavevmode\vadjust pre{\hypertarget{ref-Closs1994SpaTem}{}}%
Closs, G.P. \& Lake, P.S. (1994).
\href{https://doi.org/10.2307/2937053}{Spatial and Temporal Variation in
the Structure of an Intermittent-Stream Food Web}. \emph{Ecological
Monographs}, 64, 1--21.

\leavevmode\vadjust pre{\hypertarget{ref-deAguiar2019RevBia}{}}%
de Aguiar, M.A.M., Newman, E.A., Pires, M.M., Yeakel, J.D., Boettiger,
C., Burkle, L.A., \emph{et al.} (2019).
\href{https://doi.org/10.7717/peerj.7566}{Revealing biases in the
sampling of ecological interaction networks}. \emph{PeerJ}, 7, e7566.

\leavevmode\vadjust pre{\hypertarget{ref-Gauzens2013FooAgg}{}}%
Gauzens, B., Legendre, S., Lazzaro, X. \& Lacroix, G. (2013). Food-web
aggregation, methodological and functional issues. \emph{Oikos}, 122,
1606--1615.

\leavevmode\vadjust pre{\hypertarget{ref-Giacomuzzo2021FooWeb}{}}%
Giacomuzzo, E. \& Jordán, F. (2021).
\href{https://doi.org/10.1111/oik.08541}{Food web aggregation: Effects
on key positions}. \emph{Oikos}, 130, 2170--2181.

\leavevmode\vadjust pre{\hypertarget{ref-Griffiths1998SamEff}{}}%
Griffiths, D. (1998).
\href{https://doi.org/10.1046/j.1365-2656.1998.00244.x}{Sampling effort,
regression method, and the shape and slope of sizeabundance relations}.
\emph{Journal of Animal Ecology}, 67, 795--804.

\leavevmode\vadjust pre{\hypertarget{ref-Hadfield2014TalTwo}{}}%
Hadfield, J.D., Krasnov, B.R., Poulin, R. \& Nakagawa, S. (2014).
\href{https://doi.org/10.1086/674445}{A Tale of Two Phylogenies:
Comparative Analyses of Ecological Interactions.} \emph{The American
Naturalist}, 183, 174--187.

\leavevmode\vadjust pre{\hypertarget{ref-Havens1992ScaStr}{}}%
Havens, K. (1992).
\href{https://doi.org/10.1126/science.257.5073.1107}{Scale and Structure
in Natural Food Webs}. \emph{Science}, 257, 1107--1109.

\leavevmode\vadjust pre{\hypertarget{ref-Johnson2021BayEst}{}}%
Johnson, E.K. \& Larremore, D.B. (2021).
\href{https://doi.org/10.1101/2021.07.06.451319}{Bayesian estimation of
population size and overlap from random subsamples}.

\leavevmode\vadjust pre{\hypertarget{ref-Jordano2016SamNet}{}}%
Jordano, P. (2016).
\href{https://doi.org/10.1111/1365-2435.12763}{Sampling networks of
ecological interactions}. \emph{Functional Ecology}, 30, 1883--1893.

\leavevmode\vadjust pre{\hypertarget{ref-Joseph2020NeuHie}{}}%
Joseph, M.B. (2020). \href{https://doi.org/10.1111/ele.13462}{Neural
hierarchical models of ecological populations}. \emph{Ecology Letters},
23, 734--747.

\leavevmode\vadjust pre{\hypertarget{ref-Kenall2014OpeFut}{}}%
Kenall, A., Harold, S. \& Foote, C. (2014).
\href{https://doi.org/10.1186/1471-2148-14-66}{An open future for
ecological and evolutionary data?} \emph{BMC Evolutionary Biology}, 14,
66.

\leavevmode\vadjust pre{\hypertarget{ref-Khoshraftar2022SurGra}{}}%
Khoshraftar, S. \& An, A. (2022).
\href{https://doi.org/10.48550/arXiv.2204.01855}{A Survey on Graph
Representation Learning Methods}.

\leavevmode\vadjust pre{\hypertarget{ref-Koleff2003MeaBet}{}}%
Koleff, P., Gaston, K.J. \& Lennon, J.J. (2003).
\href{https://doi.org/10.1046/j.1365-2656.2003.00710.x}{Measuring beta
diversity for presenceabsence data}. \emph{Journal of Animal Ecology},
72, 367--382.

\leavevmode\vadjust pre{\hypertarget{ref-Kopelke2017FooStr}{}}%
Kopelke, J.-P., Nyman, T., Cazelles, K., Gravel, D., Vissault, S. \&
Roslin, T. (2017). \href{https://doi.org/10.1002/ecy.1832}{Food-web
structure of willow-galling sawflies and their natural enemies across
Europe}. \emph{Ecology}, 98, 1730--1730.

\leavevmode\vadjust pre{\hypertarget{ref-MacDonald2020RevLin}{}}%
MacDonald, A.A.M., Banville, F. \& Poisot, T. (2020).
\href{https://doi.org/10.1016/j.patter.2020.100079}{Revisiting the
Links-Species Scaling Relationship in Food Webs}. \emph{Patterns}, 1.

\leavevmode\vadjust pre{\hypertarget{ref-Makiola2020KeyQue}{}}%
Makiola, A., Compson, Z.G., Baird, D.J., Barnes, M.A., Boerlijst, S.P.,
Bouchez, A., \emph{et al.} (2020). Key Questions for Next-Generation
Biomonitoring. \emph{Frontiers in Environmental Science}, 7.

\leavevmode\vadjust pre{\hypertarget{ref-Martinez1999EffSam}{}}%
Martinez, N.D., Hawkins, B.A., Dawah, H.A. \& Feifarek, B.P. (1999).
\href{https://doi.org/10.1890/0012-9658(1999)080\%5B1044:EOSEOC\%5D2.0.CO;2}{Effects
of Sampling Effort on Characterization of Food-Web Structure}.
\emph{Ecology}, 80, 1044--1055.

\leavevmode\vadjust pre{\hypertarget{ref-McLeod2021SamAsy}{}}%
McLeod, A., Leroux, S.J., Gravel, D., Chu, C., Cirtwill, A.R., Fortin,
M.-J., \emph{et al.} (2021).
\href{https://doi.org/10.1111/oik.08650}{Sampling and asymptotic network
properties of spatial multi-trophic networks}. \emph{Oikos}, 130,
2250--2259.

\leavevmode\vadjust pre{\hypertarget{ref-Moore2016OptEco}{}}%
Moore, A.L. \& McCarthy, M.A. (2016).
\href{https://doi.org/10.1111/2041-210X.12564}{Optimizing ecological
survey effort over space and time}. \emph{Methods in Ecology and
Evolution}, 7, 891--899.

\leavevmode\vadjust pre{\hypertarget{ref-Niedballa2019AssAna}{}}%
Niedballa, J., Wilting, A., Sollmann, R., Hofer, H. \& Courtiol, A.
(2019). \href{https://doi.org/10.1002/rse2.107}{Assessing analytical
methods for detecting spatiotemporal interactions between species from
camera trapping data}. \emph{Remote Sensing in Ecology and
Conservation}, 5, 272--285.

\leavevmode\vadjust pre{\hypertarget{ref-Paine1988RoaMap}{}}%
Paine, R.T. (1988). \href{https://doi.org/10.2307/1941141}{Road Maps of
Interactions or Grist for Theoretical Development?} \emph{Ecology}, 69,
1648--1654.

\leavevmode\vadjust pre{\hypertarget{ref-Poisot2022GuiPre}{}}%
Poisot, T. (2022).
\href{https://doi.org/10.32942/osf.io/aty7n}{Guidelines for the
prediction of species interactions through binary classification}.

>>>>

%
\href{https://orcid.org/0000-0002-6506-6487}{Michael D.\,Catchen}%
%
\,\textsuperscript{1,2}\quad %
\href{https://orcid.org/0000-0002-0735-5184}{Timothée\,Poisot}%
%
\,\textsuperscript{3,2}\quad %
\href{https://orcid.org/0000-0002-6004-4027}{Laura\,Pollock}%
%
\,\textsuperscript{1,2}\quad %
\href{https://orcid.org/0000-0001-6075-8081}{Andrew\,Gonzalez}%
%
\,\textsuperscript{1,2}

@@

\vfill
Ecosystems are composed of networks of interacting species. These
interactions allow communities of species to persist through time
through both neutral and adaptive processes. Still a robust
understanding of, and ability to predict and forecast interactions among
species and their consequences for network structure remains elusive.
This knowledge-gap is largely driven by a shortfall of data---although
species occurrence data has rapidly increased in the last decade,
species interaction data has not kept pace, largely due to the intrinsic
difficulty and effort required to sample interactions. These sampling
challenges bias data and hinder inferences about the structure and
dynamics of interactions networks. Here, we demonstrate the realized
false-negative rate (the percentage of species that actually interact
but for which we do not yet have a record) can be quite high, even in
thoroughly sampled systems, due to the intrinsic variation in abundances
across species in a community. We demonstrate how a null model of
occurrence detection can be used to estimate the false-negative rate in
a given dataset. One hypothesis is that interactions between ``rare''
species are themselves rare because these species are less likely to
encounter one-another than species of higher relative abundance.
However, we demonstrate that across several datasets of spatial or
temporally replicated networks, there are positive associations that
suggest these interactions actually exist but just are not observed.
Finally, we assess how false negatives influence various models of
network prediction, and recommend directly accounting for observation
error in predictive models. We conclude by discussing how the
understanding of false-negatives can inform how we design monitoring
schemes for species interactions.

@@

\hypertarget{tbl:id}{}
\begin{longtable}[]{@{}ccccccccc@{}}
\caption{\label{tbl:id}This table describes the datasets used in the
above analysis (Fig 2). The table reports the type of each dataset, the
total number of networks in each dataset \((N)\), the total species
richness in each dataset \((S)\), the connectance of each metaweb (all
interactions across the entire spatial-temporal extent) \((C)\), the
mean species richness across each local network \(S\), the mean
connectance of each local network \(C\), the mean \(\beta\)-diversity
among overlapping species across all pairs of network species
(\(\bar{\beta}_{OS}\)), and the mean \(\beta\)-diversity among all
species in the metaweb (\(\bar{\beta}_{WN}\)). Both metrics are computed
using KGL \(\beta\)-diversity (Koleff \emph{et al.}
2003)}\tabularnewline
\toprule
Network & Type & \(N\) & \(S\) & \(C\) & \(\bar{S}\) & \(\bar{C}\) &
\(\bar{\beta}_{OS}\) & \(\bar{\beta}_{WN}\)\tabularnewline
\midrule
\endfirsthead
\toprule
Network & Type & \(N\) & \(S\) & \(C\) & \(\bar{S}\) & \(\bar{C}\) &
\(\bar{\beta}_{OS}\) & \(\bar{\beta}_{WN}\)\tabularnewline
\midrule
\endhead
Kopelke \emph{et al.} (2017) & Food Web & 100 & 98 & 0.037 & 7.87 &
0.142 & 1.383 & 1.972\tabularnewline
Thompson \& Townsend (2000) & Food Web & 18 & 566 & 0.014 & 80.67 &
0.049 & 1.617 & 1.594\tabularnewline
Havens (1992) & Food Web & 50 & 188 & 0.065 & 33.58 & 0.099 & 1.468 &
1.881\tabularnewline
Ponisio \emph{et al.} (2017) & Pollinator & 100 & 226 & 0.079 & 23.0 &
0.056 & 1.436 & 1.870\tabularnewline
Hadfield \emph{et al.} (2014) & Host-Parasite & 51 & 327 & 0.085 & 32.71
& 0.337 & 1.477 & 1.952\tabularnewline
Closs \& Lake (1994) & Food Web & 12 & 61 & 0.14 & 29.09 & 0.080 & 1.736
& 1.864\tabularnewline
CaraDonna \emph{et al.} (2017) & Pollinator & 86 & 122 & 0.18 & 21.42 &
0.312 & 1.527 & 1.907\tabularnewline
\bottomrule
\end{longtable}

@@

A better understanding of how false-negatives impact our inference of
network structure and dynamics is prediction of ecological networks by
both using information about individual species interactions and the
structure of metawebs on large scales is a practical necessity.
False-negatives could pose a problem for many forms of inference in
network ecology. For example, inferring the structural or dynamic
stability of a network could be prone to error if the observed network
is not sampled ``enough.'' What exactly ``enough'' means is then
specific to the application, and should be assessed via methods like
those here when designing samples. Further, predictions about network
rewiring (Thompson \& Gonzalez 2017) due to range shifts in response to
climate change could be error-prone without accounting for interactions
that have not been observed but that still may become climatically
infeasible. As is evident from Figure 1(A), we can never guarantee there
are no false-negatives in data. In recent years, there has been interest
toward explicitly accounting for false-negatives in models (Stock
\emph{et al.} 2017; Young \emph{et al.} 2021), and a predictive approach
to networks---rather than expecting our samples to fully capture all
interactions (Strydom \emph{et al.} 2021). As a result, better models
for predicting interactions are needed for interaction networks. This
includes explicitly accounting for observation error (Johnson \&
Larremore 2021)---certain classes of models have been used to reflect
hidden states which account for detection error in occupancy modeling
(Joseph 2020), and could be integrated in the predictive models of
interactions in the future.

@@

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\hypertarget{ref-Banville2021ManJl}{}%
Banville, F., Vissault, S. \& Poisot, T. (2021). Mangal.jl and
EcologicalNetworks.jl: Two complementary packages for analyzing
ecological networks in Julia. \emph{Journal of Open Source Software}, 6,
2721.

\leavevmode\hypertarget{ref-Bascompte2007PlaMut}{}%
Bascompte, J. \& Jordano, P. (2007). Plant-Animal Mutualistic Networks:
The Architecture of Biodiversity. \emph{Annual Review of Ecology,
Evolution, and Systematics}, 38, 567--593.

\leavevmode\hypertarget{ref-Becker2021OptPre}{}%
Becker, D.J., Albery, G.F., Sjodin, A.R., Poisot, T., Bergner, L.M.,
Dallas, T.A., \emph{et al.} (2021). Optimizing predictive models to
prioritize viral discovery in zoonotic reservoirs.

\leavevmode\hypertarget{ref-Bezanson2015JulFre}{}%
Bezanson, J., Edelman, A., Karpinski, S. \& Shah, V.B. (2015). Julia: A
Fresh Approach to Numerical Computing.

\leavevmode\hypertarget{ref-Blanchet2020CooNot}{}%
Blanchet, F.G., Cazelles, K. \& Gravel, D. (2020). Co-occurrence is not
evidence of ecological interactions. \emph{Ecology Letters}, 23,
1050--1063.

\leavevmode\hypertarget{ref-Blaom2020MljJul}{}%
Blaom, A.D., Kiraly, F., Lienart, T., Simillides, Y., Arenas, D. \&
Vollmer, S.J. (2020). MLJ: A Julia package for composable machine
learning. \emph{Journal of Open Source Software}, 5, 2704.

\leavevmode\hypertarget{ref-Boakes2015InfSpe}{}%
Boakes, E.H., Rout, T.M. \& Collen, B. (2015). Inferring species
extinction: The use of sighting records. \emph{Methods in Ecology and
Evolution}, 6, 678--687.

\leavevmode\hypertarget{ref-Canard2012EmeStr}{}%
Canard, E., Mouquet, N., Marescot, L., Gaston, K.J., Gravel, D. \&
Mouillot, D. (2012). Emergence of Structural Patterns in Neutral Trophic
Networks. \emph{PLOS ONE}, 7, e38295.

\leavevmode\hypertarget{ref-CaraDonna2017IntRew}{}%
CaraDonna, P.J., Petry, W.K., Brennan, R.M., Cunningham, J.L.,
Bronstein, J.L., Waser, N.M., \emph{et al.} (2017). Interaction rewiring
and the rapid turnover of plantpollinator networks. \emph{Ecology
Letters}, 20, 385--394.

\leavevmode\hypertarget{ref-Carlson2020WhaWou}{}%
Carlson, C.J., Dallas, T.A., Alexander, L.W., Phelan, A.L. \& Phillips,
A.J. (2020). What would it take to describe the global diversity of
parasites? \emph{Proceedings of the Royal Society B: Biological
Sciences}, 287, 20201841.

\leavevmode\hypertarget{ref-Cazelles2016TheSpe}{}%
Cazelles, K., Araújo, M.B., Mouquet, N. \& Gravel, D. (2016). A theory
for species co-occurrence in interaction networks. \emph{Theoretical
Ecology}, 9, 39--48.

\leavevmode\hypertarget{ref-Closs1994SpaTem}{}%
Closs, G.P. \& Lake, P.S. (1994). Spatial and Temporal Variation in the
Structure of an Intermittent-Stream Food Web. \emph{Ecological
Monographs}, 64, 1--21.

\leavevmode\hypertarget{ref-deAguiar2019RevBia}{}%
de Aguiar, M.A.M., Newman, E.A., Pires, M.M., Yeakel, J.D., Boettiger,
C., Burkle, L.A., \emph{et al.} (2019). Revealing biases in the sampling
of ecological interaction networks. \emph{PeerJ}, 7, e7566.

\leavevmode\hypertarget{ref-Gauzens2013FooAgg}{}%
Gauzens, B., Legendre, S., Lazzaro, X. \& Lacroix, G. (2013). Food-web
aggregation, methodological and functional issues. \emph{Oikos}, 122,
1606--1615.

\leavevmode\hypertarget{ref-Giacomuzzo2021FooWeb}{}%
Giacomuzzo, E. \& Jordán, F. (2021). Food web aggregation: Effects on
key positions. \emph{Oikos}, 130, 2170--2181.

\leavevmode\hypertarget{ref-Griffiths1998SamEff}{}%
Griffiths, D. (1998). Sampling effort, regression method, and the shape
and slope of sizeabundance relations. \emph{Journal of Animal Ecology},
67, 795--804.

\leavevmode\hypertarget{ref-Hadfield2014TalTwo}{}%
Hadfield, J.D., Krasnov, B.R., Poulin, R. \& Nakagawa, S. (2014). A Tale
of Two Phylogenies: Comparative Analyses of Ecological Interactions.
\emph{The American Naturalist}, 183, 174--187.

\leavevmode\hypertarget{ref-Havens1992ScaStr}{}%
Havens, K. (1992). Scale and Structure in Natural Food Webs.
\emph{Science}, 257, 1107--1109.

\leavevmode\hypertarget{ref-Johnson2021BayEst}{}%
Johnson, E.K. \& Larremore, D.B. (2021). Bayesian estimation of
population size and overlap from random subsamples.

\leavevmode\hypertarget{ref-Jordano2016SamNet}{}%
Jordano, P. (2016). Sampling networks of ecological interactions.
\emph{Functional Ecology}, 30, 1883--1893.

\leavevmode\hypertarget{ref-Joseph2020NeuHie}{}%
Joseph, M.B. (2020). Neural hierarchical models of ecological
populations. \emph{Ecology Letters}, 23, 734--747.

\leavevmode\hypertarget{ref-Kenall2014OpeFut}{}%
Kenall, A., Harold, S. \& Foote, C. (2014). An open future for
ecological and evolutionary data? \emph{BMC Evolutionary Biology}, 14,
66.

\leavevmode\hypertarget{ref-Khoshraftar2022SurGra}{}%
Khoshraftar, S. \& An, A. (2022). A Survey on Graph Representation
Learning Methods.

\leavevmode\hypertarget{ref-Koleff2003MeaBet}{}%
Koleff, P., Gaston, K.J. \& Lennon, J.J. (2003). Measuring beta
diversity for presenceabsence data. \emph{Journal of Animal Ecology},
72, 367--382.

\leavevmode\hypertarget{ref-Kopelke2017FooStr}{}%
Kopelke, J.-P., Nyman, T., Cazelles, K., Gravel, D., Vissault, S. \&
Roslin, T. (2017). Food-web structure of willow-galling sawflies and
their natural enemies across Europe. \emph{Ecology}, 98, 1730--1730.

\leavevmode\hypertarget{ref-MacDonald2020RevLin}{}%
MacDonald, A.A.M., Banville, F. \& Poisot, T. (2020). Revisiting the
Links-Species Scaling Relationship in Food Webs. \emph{Patterns}, 1.

\leavevmode\hypertarget{ref-Makiola2020KeyQue}{}%
Makiola, A., Compson, Z.G., Baird, D.J., Barnes, M.A., Boerlijst, S.P.,
Bouchez, A., \emph{et al.} (2020). Key Questions for Next-Generation
Biomonitoring. \emph{Frontiers in Environmental Science}, 7.

\leavevmode\hypertarget{ref-Martinez1999EffSam}{}%
Martinez, N.D., Hawkins, B.A., Dawah, H.A. \& Feifarek, B.P. (1999).
Effects of Sampling Effort on Characterization of Food-Web Structure.
\emph{Ecology}, 80, 1044--1055.

\leavevmode\hypertarget{ref-McLeod2021SamAsy}{}%
McLeod, A., Leroux, S.J., Gravel, D., Chu, C., Cirtwill, A.R., Fortin,
M.-J., \emph{et al.} (2021). Sampling and asymptotic network properties
of spatial multi-trophic networks. \emph{Oikos}, 130, 2250--2259.

\leavevmode\hypertarget{ref-Moore2016OptEco}{}%
Moore, A.L. \& McCarthy, M.A. (2016). Optimizing ecological survey
effort over space and time. \emph{Methods in Ecology and Evolution}, 7,
891--899.

\leavevmode\hypertarget{ref-Niedballa2019AssAna}{}%
Niedballa, J., Wilting, A., Sollmann, R., Hofer, H. \& Courtiol, A.
(2019). Assessing analytical methods for detecting spatiotemporal
interactions between species from camera trapping data. \emph{Remote
Sensing in Ecology and Conservation}, 5, 272--285.

\leavevmode\hypertarget{ref-Paine1988RoaMap}{}%
Paine, R.T. (1988). Road Maps of Interactions or Grist for Theoretical
Development? \emph{Ecology}, 69, 1648--1654.

\leavevmode\hypertarget{ref-Poisot2022GuiPre}{}%
Poisot, T. (2022). Guidelines for the prediction of species interactions
through binary classification.

\leavevmode\hypertarget{ref-Poisot2021GloKno}{}%
Poisot, T., Bergeron, G., Cazelles, K., Dallas, T., Gravel, D.,
MacDonald, A., \emph{et al.} (2021). Global knowledge gaps in species
interaction networks data. \emph{Journal of Biogeography}, 48,
1552--1563.

\leavevmode\hypertarget{ref-Poisot2022NetEmb}{}%
Poisot, T., Ouellet, M.-A., Mollentze, N., Farrell, M.J., Becker, D.J.,
Brierly, L., \emph{et al.} (2022). Network embedding unveils the hidden
interactions in the mammalian virome.

\leavevmode\hypertarget{ref-Poisot2015SpeWhy}{}%
Poisot, T., Stouffer, D.B. \& Gravel, D. (2015). Beyond species: Why
ecological interaction networks vary through space and time.
\emph{Oikos}, 124, 243--251.

\leavevmode\hypertarget{ref-Ponisio2017OppAtt}{}%
Ponisio, L.C., Gaiarsa, M.P. \& Kremen, C. (2017). Opportunistic
attachment assembles plantpollinator networks. \emph{Ecology Letters},
20, 1261--1272.

\leavevmode\hypertarget{ref-Savage2004EffBod}{}%
Savage, V.M., Gillooly, J.F., Brown, J.H., West, G.B. \& Charnov, E.L.
(2004). Effects of Body Size and Temperature on Population Growth.
\emph{The American Naturalist}, 163, 429--441.

\leavevmode\hypertarget{ref-Song2022GenDri}{}%
Song, C., Simmons, B.I., Fortin, M.-J. \& Gonzalez, A. (2022).
Generalism drives abundance: A computational causal discovery approach.
\emph{PLOS Computational Biology}, 18, e1010302.

\leavevmode\hypertarget{ref-Stephenson2020TecAdv}{}%
Stephenson, P. (2020). Technological advances in biodiversity
monitoring: Applicability, opportunities and challenges. \emph{Current
Opinion in Environmental Sustainability}, Open issue 2020 part A:
Technology Innovations and Environmental Sustainability in the
Anthropocene, 45, 36--41.

\leavevmode\hypertarget{ref-Stock2017LinFil}{}%
Stock, M., Poisot, T., Waegeman, W. \& De Baets, B. (2017). Linear
filtering reveals false negatives in species interaction data.
\emph{Scientific Reports}, 7, 45908.

\leavevmode\hypertarget{ref-Strydom2021RoaPre}{}%
Strydom, T., Catchen, M.D., Banville, F., Caron, D., Dansereau, G.,
Desjardins-Proulx, P., \emph{et al.} (2021). A roadmap towards
predicting species interaction networks (across space and time).
\emph{Philosophical Transactions of the Royal Society B: Biological
Sciences}, 376, 20210063.

\leavevmode\hypertarget{ref-Thompson2017DisGov}{}%
Thompson, P.L. \& Gonzalez, A. (2017). Dispersal governs the
reorganization of ecological networks under environmental change.
\emph{Nature Ecology \& Evolution}, 1, 1--8.

\leavevmode\hypertarget{ref-Thompson2000ResSol}{}%
Thompson, R.M. \& Townsend, C.R. (2000). Is resolution the solution?:
The effect of taxonomic resolution on the calculated properties of three
stream food webs. \emph{Freshwater Biology}, 44, 413--422.
